Canonical rings of $\bq$-divisors on projective space and Hirzebruch surfaces

### 2015-07-16 surfaces-write-up/surface-write-up.tex
edits to 5.3

Note that we can view a relation from Equation
~\ref{eqn:hirz-relations-psi} as an element of $S$ given
by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  Let $S'\subseteq (\mathbb{R}_{\ge 0})^{n+1}$ be the
set of $(d, r_1, \ldots, r_{i-1}, r_i + 1, r_{i+1}, \ldots , r_n)$ satisfying $r_i \ge -\alpha_i d$,
$\bida_i + \sum_{j = 1}^m \bida_j c_j = 0$, and $\bidb_i + \sum_{j=1}^n \bidb_j c_j
= 0$.  A careful computation deduces that $\gamma \in S'$ is of the form 
\[
	E + \sum_{k\in \Te} r_k e_k + \sum_{\substack{h \in \Tp \\ k \in \Tm}} r_{h,k} e_{h,k}
\]

\noindent
where $E$ is $\mathbb{R}_{\ge 0}$
combination of elements in 
\[
	\{e_i \mbox{ if } i \in S\} \cup \{e_{i, j}: j \in \Tm \mbox{ if }
	i	\in \Tp \} \cup \{e_{j, i}: j \in \Tp \mbox{ if } i \in \Tm \}.
\]

>>>>

%Note that we can view a relation from Equation
%~\ref{eqn:hirz-relations-psi} as an element of $S$ given
%by $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$.  
Let $S'\subseteq S$ be the
set of $(d, c_1, \ldots, c_{i-1}, c_i + 1, c_{i+1}, \ldots , c_n)$ satisfying $c_i \ge -\alpha_i d$,
$\bida_i + \sum_{j = 1}^m \bida_j c_j = 0$, and $\bidb_i + \sum_{j=1}^n \bidb_j c_j
= 0$.  A careful computation deduces that the lattice point corresponding to $y_i \prod_{j=1}^n {y_j}^{c_j}$ is of the form 
\[
	E + \sum_{k\in \Te} r_k e_k + \sum_{\substack{h \in \Tp \\ k \in \Tm}} r_{h,k} e_{h,k}
\]

\noindent
where $E$ is in degree $\mathbb{R}_{\ge 0}$
combination of elements in 
\[
	\{e_j: j\in \{i\} \cap S\} \cup \{e_{i, j}: j \in \Tm \mbox{ if }
	i	\in \Tp \} \cup \{e_{j, i}: j \in \Tp \mbox{ if } i \in \Tm \}.
\]
